DOM bridges and barriers: systematic review and survey

### 2025-10-15 reports/draft_results.qmd
math error oops

#radar plots
freq_job_survey3 <- freq_job_survey %>%
  # group_by(fish_ship, bridge_barr) %>%
  # mutate(n_total = sum(total)) %>%
  # ungroup() %>%
  # group_by(fish_ship, bridge_barr, code_name) %>%
  # mutate(n_subtotal = sum(total)) %>%
  # reframe(value = (n_subtotal/n_total)*100) %>%
  # ungroup() %>%
  mutate(id = paste(fish_ship, bridge_barr, code_name)) %>%
  distinct(id, .keep_all = TRUE) %>%
  select(-c(id)) %>%
  group_by(fish_ship, bridge_barr, code_name) %>%
  summarise(value = sum(total))

@@

ggradar::ggradar(top_bridge,
        values.radar = c(0, 2, 4), 
        background.circle.colour = "white",
        axis.line.colour = "gray60",
        gridline.min.colour = "gray60",
        gridline.mid.colour = "gray60",
        gridline.max.colour = "gray60",
        group.colours = c("#F29325", "#007172"),#007172
        legend.position = "bottom", 
        fill = TRUE, 
        axis.label.size = 3)

@@

ggradar::ggradar(top_barrier,
        values.radar = c(0, 1, 3), 
        background.circle.colour = "white",
        axis.line.colour = "gray60",
        gridline.min.colour = "gray60",
        gridline.mid.colour = "gray60",
        gridline.max.colour = "gray60",
        group.colours = c("#F29325", "#007172"),#007172
        legend.position = "none", 
        fill = TRUE, 
        axis.label.size = 3)

@@

#radar plots
freq_job_lit3 <- freq_job_lit %>%
  # group_by(fish_ship, bridge_barr) %>%
  # mutate(n_total = sum(total)) %>%
  # ungroup() %>%
  # group_by(fish_ship, bridge_barr, code_name) %>% 
  # mutate(n_subtotal = sum(total)) %>%
  # reframe(value = (n_subtotal/n_total)*100) %>%
  # ungroup() %>%
  mutate(id = paste(fish_ship, bridge_barr, code_name)) %>%
  distinct(id, .keep_all = TRUE) %>%
  select(-c(id)) %>%
  group_by(fish_ship, bridge_barr, code_name) %>%
  summarise(value = sum(total))

@@

ggradar::ggradar(top_bridge,
        values.radar = c(0, 15, 30), 
        background.circle.colour = "white",
        axis.line.colour = "gray60",
        gridline.min.colour = "gray60",
        gridline.mid.colour = "gray60",
        gridline.max.colour = "gray60",
        group.colours = c("#F29325", "#007172"),
        legend.position = "bottom", 
        fill = TRUE, 
        axis.label.size = 3)

@@

ggradar::ggradar(top_barrier,
        values.radar = c(0, 15, 30), 
        background.circle.colour = "white",
        axis.line.colour = "gray60",
        gridline.min.colour = "gray60",
        gridline.mid.colour = "gray60",
        gridline.max.colour = "gray60",
        group.colours = c("#F29325", "#007172"),
        legend.position = "none", 
        fill = TRUE, 
        axis.label.size = 3)

#ggsave("figures/ms_figs/industry/radar_ba_lit.png", height = 8, width = 8, units = c("in"))

>>>>

#radar plots
freq_job_survey3 <- freq_job_survey %>%
  # group_by(fish_ship, bridge_barr) %>%
  # mutate(n_total = sum(total)) %>%
  # ungroup() %>%
  # group_by(fish_ship, bridge_barr, code_name) %>%
  # mutate(n_subtotal = sum(total)) %>%
  # reframe(value = (n_subtotal/n_total)*100) %>%
  # ungroup() %>%
  #mutate(id = paste(fish_ship, bridge_barr, code_name)) %>%
  #distinct(id, .keep_all = TRUE) %>%
  #select(-c(id))
  group_by(fish_ship, bridge_barr, code_name) %>%
  summarise(value = sum(total))

@@

ggradar::ggradar(top_bridge,
        values.radar = c(0, 5, 10), 
        background.circle.colour = "white",
        axis.line.colour = "gray60",
        gridline.min.colour = "gray60",
        gridline.mid.colour = "gray60",
        gridline.max.colour = "gray60",
        group.colours = c("#F29325", "#007172"),#007172
        legend.position = "bottom", 
        fill = TRUE, 
        axis.label.size = 3)

@@

ggradar::ggradar(top_barrier,
        values.radar = c(0, 3, 6), 
        background.circle.colour = "white",
        axis.line.colour = "gray60",
        gridline.min.colour = "gray60",
        gridline.mid.colour = "gray60",
        gridline.max.colour = "gray60",
        group.colours = c("#F29325", "#007172"),#007172
        legend.position = "none", 
        fill = TRUE, 
        axis.label.size = 3)

@@

#radar plots
freq_job_lit3 <- freq_job_lit %>%
  # group_by(fish_ship, bridge_barr) %>%
  # mutate(n_total = sum(total)) %>%
  # ungroup() %>%
  # group_by(fish_ship, bridge_barr, code_name) %>% 
  # mutate(n_subtotal = sum(total)) %>%
  # reframe(value = (n_subtotal/n_total)*100) %>%
  # ungroup() %>%
  # mutate(id = paste(fish_ship, bridge_barr, code_name)) %>%
  # distinct(id, .keep_all = TRUE) %>%
  # select(-c(id)) %>%
  group_by(fish_ship, bridge_barr, code_name) %>%
  summarise(value = sum(total))

@@

ggradar::ggradar(top_bridge,
        values.radar = c(0, 20, 40), 
        background.circle.colour = "white",
        axis.line.colour = "gray60",
        gridline.min.colour = "gray60",
        gridline.mid.colour = "gray60",
        gridline.max.colour = "gray60",
        group.colours = c("#F29325", "#007172"),
        legend.position = "bottom", 
        fill = TRUE, 
        axis.label.size = 3)

@@

ggradar::ggradar(top_barrier,
        values.radar = c(0, 15, 35), 
        background.circle.colour = "white",
        axis.line.colour = "gray60",
        gridline.min.colour = "gray60",
        gridline.mid.colour = "gray60",
        gridline.max.colour = "gray60",
        group.colours = c("#F29325", "#007172"),
        legend.position = "none", 
        fill = TRUE, 
        axis.label.size = 3)

ggsave("figures/ms_figs/industry/radar_ba_lit.png", height = 8, width = 8, units = c("in"))
